Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-07-17 2016-Weak-FH-Bisim/WeakBisim.tex
lemma 6, qques ajouts

\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT}, denoting $\displaystyle{J=\bigcup_{i=0}^{m_1}J_{1i}\cup J_2\cup \bigcup_{i=0}^{m_2}J_{3i}}$, we can conclude from cases 1, 2 and 3 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				(\gamma_j')^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha''}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}
where:\\
$\alpha''=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}$

We have:
$\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}=\alpha''\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}$.\\
As $\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}$ has no effect on variables of $P$ and thus on variables of $\alpha$, we have $\alpha=\alpha''$.
\\
 for all $l\in L$: 
$s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l$
and \\%$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\}$,\\
${(\gamma_j')}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
~~\qquad \mybigdotcup_{i=0}^{m_2}
\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}} }\\
\Pred\,'=\bigwedge_{i=0}^{m_1}\Pred'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}\land\Pred'_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}\land\\ 
~\qquad\qquad\bigwedge_{i=0}^{m_2}\Pred'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}\\
\Post'=\bigotimes_{j=m_2}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}$

@@

Indeed, \TODO{fill the empty lines (more complex but easy adaptation)}
{\scriptsize \begin{equation*}
\begin{split}
\Pred&\iff\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\land
\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
&\iff\bigwedge_{i=0}^{m_1}\left(\Pred'_{1p}
		\land {\Pred''_{1p}}\land \alpha_{1p}=\beta_{1pj_0}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\right)\\
&\qquad\land\\
&\qquad\land\\
&\iff\bigwedge_{i=0}^{m_1}\left((\Pred'_{1p}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}})
		\land ({\Pred''_{1p}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post''_{1j}})\land (\alpha_{1p}=\beta_{1pj_0}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}})\right)\\
&\qquad\land\\
&\qquad\land\\
&\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\bigotimes_{j=k-1}^{0}\!\!\Post_{j}\land\Pred_\beta
\\&\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\bigotimes_{j=k-1}^{0}\!\!\Post_{j}\land
(\gamma_{j_0}=[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n]])
\end{split}\end{equation*}
}
Which is exactly what is needed.

Finally we have

@@

&=\bigotimes_{j=m_2}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}\\
&\qquad \uplus \bigotimes_{j=m_2}^{0}\!\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}\\

>>>>

\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT}, and denoting $\displaystyle{J=\bigcup_{i=0}^{m_1}J_{1i}\cup J_2\cup \bigcup_{i=0}^{m_2}J_{3i}}$, we can conclude from cases 1, 2 and 3 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				(\gamma_j')^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha''}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}
where:\\
$\alpha''=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}$\\
On the other hand, we have:
$\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}=\alpha''\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}$.\\
As $\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}$ has no effect on variables of $P$ and thus on variables of $\alpha$, so we have $\alpha=\alpha''$.
\\
For all $l\in L$: 
$s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l$
and \\%$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\}$,\\
${(\gamma_j')}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
~~\qquad \qquad\qquad\qquad\qquad \mybigdotcup_{i=0}^{m_2}
\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}} }\\
\Pred\,'=\bigwedge_{i=0}^{m_1}\Pred'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}\land\Pred'_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}\land\\ 
~\qquad\qquad\bigwedge_{i=0}^{m_2}\Pred'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}\\
\Post'=\bigotimes_{j=m_2}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}$

@@

Indeed, \TODO{fill the empty lines (more complex but easy adaptation)}
{\scriptsize \begin{equation*}
\Pred&\iff\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\land
\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
&\iff\bigwedge_{i=0}^{m_1}\left(\Pred'_{1p}
		\land {\Pred''_{1p}}\land \alpha_{1p}=\beta_{1pj_0}\right)\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}} \\
&\qquad\land\left(\Pred'_{2}
		\land {\Pred''_{2}}\land \alpha_{2}=\beta_{2j_0}\right)\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
&\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred'_{3p}
		\land {\Pred''_{3p}}\land \alpha_{3p}=\beta_{3pj_0}\right) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
&\iff\bigwedge_{i=0}^{m_1}\left((\Pred'_{1p}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}})
		\land ({\Pred''_{1p}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post''_{1j}})\land (\alpha_{1p}=\beta_{1pj_0})\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\right) \\
&\qquad\land \left(\Pred'_{2}\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}
		\land {\Pred''_{2}} \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \land (\alpha_{2}=\beta_{2j_0})\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \right) \\
&\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred'_{3p} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} 
		\land {\Pred''_{3p}} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \right ) \\
		 & \qquad \land (\alpha_{3p}=\beta_{3pj_0}) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}  \\
&\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\bigotimes_{j=k-1}^{0}\!\!\Post_{j}\land\Pred_\beta
\\&\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\bigotimes_{j=k-1}^{0}\!\!\Post_{j}\land
(\gamma_{j_0}=[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n]])
\end{split}\end{equation*}
which is exactly what is needed.\\
Finally we have:

@@

&=\bigotimes_{j=m_2}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j} \uplus \bigotimes_{j=m_2}^{0}\!\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}\\
